18Q4

### 2019-03-05 18Q4.Rmd
renamed Rmds to separate DepMap releases more clearly

---
title: "Manuscript"
author: "Sally Claridge"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: cerulean
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
    code_folding: hide
    pandoc_args: [
      "+RTS", "-K2048m",
      "-RTS"
    ]
---

Analysis of the Broad's Avana CRISPR (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017) and the Broad and Dana-Farber Cancer Institite's Achilles shRNA (MacFarland et al. 2018, Data Science 2018).

@@

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
```

>>>>

---
title: "18Q4"
author: "Sally Claridge"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: cerulean
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
    code_folding: hide
    pandoc_args: [
      "+RTS", "-K2048m",
      "-RTS"
    ]
---

Analysis of the Broad's Avana CRISPR (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017), the Cancer Therapeutics Response Portal (CTRP) drug screen dataset (v2) (Basu et al., 2013; M. G. Rees et al., 2016; B. Seashore-Ludlow et al., 2015), the Genomics of Drug Sensitivity in Cancer (GDSC) drug screen dataset (Garnett et al., 2012; Yang et al., 2012) , and the Cancer Cell Line Encyclopedia (CCLE) drug screen dataset (J. Barretina et al., 2012; T. C. C. L. E. Consortium & Consortium, 2015).

@@

This comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
```
